<i>invivoPKfit</i> and <i>CvTdb</i> figures

### 2022-12-01 MainAnalysis.Rmd
Properly vectorized cp_1comp and cp_2comp. No more need for fitfun() and analytic_model_fun() as intermediaries -- log_likelihood() now directly calls the analytic model function or httk::solve_1comp(). Also, in analyze_subset(), when repeating optimization with smaller convergence tolerance, starts from previous set of best-fit params.

### do 1-Compartment fit
system.time(PK.fit.table.1comp <- fit_all(
  data.set = cvt.data,
  model = "1compartment",
  modelfun = "analytic",
  compound.col = "analyte_name_original",
  dtxsid.col = "dsstox_substance_id",
  cas.col = "dsstox_casrn",
  reference.col = "fk_reference_document_id",
  species.col = "species",
  species.weight.col = "weight_kg",
  species.weight.units.default = "kg",
  dose.col = "dose_level_normalized",
  time.col = "time_hr",
  time.units.default = "hr",
  media.col = "conc_medium_normalized",
  media.units.default = "normalized",
  value.col = "conc",
  units.default = NA,
  route.col = "administration_route_normalized",
  source.col = "document_id",
  loq.col ="calc_loq",
  subject.default = NA,
  info.default = NA,
  suppress.messages = FALSE
))

write.csv(PK.fit.table.1comp,
          paste("inst/ext/PK_fit_table_1comp_",
                                    format(Sys.time(), "%Y_%m_%d_%H_%M_%S"),
                                    ".csv",
                                    sep=""),
          row.names = FALSE)

@@

### do 2-Compartment fit
system.time(PK.fit.table.2comp <- fit_all(
  data.set = cvt.data,
  model = "2compartment",
  modelfun = "analytic",
  compound.col = "analyte_name_original",
  dtxsid.col = "dsstox_substance_id",
  cas.col = "dsstox_casrn",
  reference.col = "fk_reference_document_id",
  species.col = "species",
  species.weight.col = "weight_kg",
  species.weight.units.default = "kg",
  dose.col = "dose_level_normalized",
  time.col = "time_hr",
  time.units.default = "hr",
  media.col = "conc_medium_normalized",
  media.units.default = "normalized",
  value.col = "conc",
    units.default = NA,
  route.col = "administration_route_normalized",
  source.col = "document_id",
  loq.col ="calc_loq",
  subject.default = NA,
  info.default = NA,
  suppress.messages = FALSE
))
write.csv(PK.fit.table.2comp, paste("inst/ext/PK_fit_table_2comp_",
                                    format(Sys.time(), "%Y_%m_%d_%H_%M_%S"),
                                    ".csv",
                                    sep=""), row.names = FALSE)

@@

```{r, run_invivoPKfit_flat, eval = FALSE}
### do flat fit
system.time(PK.fit.table.flat <- fit_all(
  data.set = cvt.data,
  model = "flat",
  modelfun = "analytic",
  compound.col = "analyte_name_original",
  dtxsid.col = "dsstox_substance_id",
  cas.col = "dsstox_casrn",
  reference.col = "fk_reference_document_id",
  species.col = "species",
  species.weight.col = "weight_kg",
  species.weight.units.default = "kg",
  dose.col = "dose_level_normalized",
  time.col = "time_hr",
  time.units.default = "hr",
  media.col = "conc_medium_normalized",
  media.units.default = "normalized",
  value.col = "conc",
  units.default = NA,
  route.col = "administration_route_normalized",
  source.col = "document_id",
  loq.col ="calc_loq",
  subject.default = NA,
  info.default = NA,
  suppress.messages = TRUE
))

write.csv(PK.fit.table.flat[[1]], paste("inst/ext/PK.fit.table.flat.",THIS.DATE,".csv",sep=""), row.names = FALSE)
write.csv(PK.fit.table.flat[[2]], paste("inst/ext/processed.flat.data.",THIS.DATE,".csv",sep=""), row.names = FALSE)
```

>>>>

run_timestamp <- format(Sys.time(), "%Y_%m_%d_%H_%M_%S")

### do 1-Compartment fit
system.time(
  capture.output(
    PK.fit.table.1comp <- fit_all(
      data.set = cvt.data,
      model = "1compartment",
      modelfun = "analytic",
      compound.col = "analyte_name_original",
      dtxsid.col = "dsstox_substance_id",
      cas.col = "dsstox_casrn",
      reference.col = "fk_reference_document_id",
      species.col = "species",
      species.weight.col = "weight_kg",
      species.weight.units.default = "kg",
      dose.col = "dose_level_normalized",
      time.col = "time_hr",
      time.units.default = "hr",
      media.col = "conc_medium_normalized",
      media.units.default = "normalized",
      value.col = "conc",
      units.default = NA,
      route.col = "administration_route_normalized",
      source.col = "document_id",
      loq.col ="calc_loq",
      subject.default = NA,
      info.default = NA,
      suppress.messages = FALSE
  ),
  file = paste0("inst/ext/PK_fit_table_1comp_output_",
                run_timestamp,
                ".txt"),
  type = "message"
  )
)

write.csv(PK.fit.table.1comp,
          paste("inst/ext/PK_fit_table_1comp_",
                                    run_timestamp,
                                    ".csv",
                                    sep=""),
          row.names = FALSE)

@@

run_timestamp <- format(Sys.time(), "%Y_%m_%d_%H_%M_%S")

### do 2-Compartment fit
system.time(
  capture.output(
    PK.fit.table.2comp <- fit_all(
      data.set = cvt.data,
      model = "2compartment",
      modelfun = "analytic",
      compound.col = "analyte_name_original",
      dtxsid.col = "dsstox_substance_id",
      cas.col = "dsstox_casrn",
      reference.col = "fk_reference_document_id",
      species.col = "species",
      species.weight.col = "weight_kg",
      species.weight.units.default = "kg",
      dose.col = "dose_level_normalized",
      time.col = "time_hr",
      time.units.default = "hr",
      media.col = "conc_medium_normalized",
      media.units.default = "normalized",
      value.col = "conc",
      units.default = NA,
      route.col = "administration_route_normalized",
      source.col = "document_id",
      loq.col ="calc_loq",
      subject.default = NA,
      info.default = NA,
      suppress.messages = FALSE
    ),
    file = paste0("inst/ext/PK_fit_table_2comp_output_",
                  run_timestamp,
                  ".txt"),
    type = "message"
  )
)

write.csv(PK.fit.table.2comp, paste("inst/ext/PK_fit_table_2comp_",
                                    run_timestamp,
                                    ".csv",
                                    sep=""), row.names = FALSE)

@@

```{r, run_invivoPKfit_flat, eval = FALSE}
devtools::load_all("invivopkfit")

run_timestamp <- format(Sys.time(), "%Y_%m_%d_%H_%M_%S")

system.time(
  capture.output(
    PK.fit.table.flat <- fit_all(
      data.set = cvt.data,
      model = "flat",
      modelfun = "analytic",
      compound.col = "analyte_name_original",
      dtxsid.col = "dsstox_substance_id",
      cas.col = "dsstox_casrn",
      reference.col = "fk_reference_document_id",
      species.col = "species",
      species.weight.col = "weight_kg",
      species.weight.units.default = "kg",
      dose.col = "dose_level_normalized",
      time.col = "time_hr",
      time.units.default = "hr",
      media.col = "conc_medium_normalized",
      media.units.default = "normalized",
      value.col = "conc",
      units.default = NA,
      route.col = "administration_route_normalized",
      source.col = "document_id",
      loq.col ="calc_loq",
      subject.default = NA,
      info.default = NA,
      suppress.messages = FALSE
    ),
    file = paste0("inst/ext/PK_fit_table_flat_output_",
                  run_timestamp,
                  ".txt"),
    type = "message"
  )
)

write.csv(PK.fit.table.flat, paste("inst/ext/PK_fit_table_flat_",
                                    run_timestamp,
                                    ".csv",
                                    sep=""), row.names = FALSE)
```
